---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/dhsc-govuk/PHEindicatormethods/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/dhsc-govuk/PHEindicatormethods/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/dhsc-govuk/PHEindicatormethods/graph/badge.svg)](https://app.codecov.io/gh/dhsc-govuk/PHEindicatormethods)
<!-- badges: end -->

# PHEindicatormethods

This is an R package to support analysts in the execution of statistical methods approved for use in the production of PHE indicators such as those presented via [Fingertips](https://fingertips.phe.org.uk/).  It provides functions for the generation of Proportions, Rates, DSRs, ISRs, Means, Life Expectancy and Slope Index of Inequality including confidence intervals for these statistics, and a function for assigning data to quantiles.  

In October 2021 Public Health England (PHE) was disbanded and as a result this package is now owned by the Department of Health and Social Care.  It will continue to be supported and to prevent breaking changes there are currently no immediate plans to rename the package or its functions in light of this organisational change.

Any feedback would be appreciated and can be provided using the Issues section of the [PHEindicatormethods GitHub repository](https://github.com/dhsc-govuk/PHEindicatormethods).

<br/>
<br/>

## Installation


#### Install from CRAN

Install the latest release version of PHEindicatormethods directly from CRAN with:

``` {r install from CRAN, eval=FALSE}
install.packages("PHEindicatormethods")
```

<br/>
<br/>

#### Install a development version from GitHub using remotes package

You can install a development version of PHEindicatormethods from GitHub with:

``` {r devtools-installation, eval=FALSE}
if (!require(remotes)) install.packages("remotes")

remotes::install_github("dhsc-govuk/PHEindicatormethods",
                         build_vignettes = TRUE,
                         dependencies = TRUE,
                         build_opts = c("--no-resave-data"))
```


<br/>
<br/>



## Package Versioning
Following installation of this package, type 'packageVersion("PHEindicatormethods")' in the R console to show the package version.  If it is suffixed with a 9000 number then you are using an unapproved development version.

Released versions of this package will have version numbers consisting of three parts:  

major.minor.patch  

In-development versions of this package will have a fourth component, the development version number, which will increment from 9000.

See https://r-pkgs.org/lifecycle.html for further information on package versioning




